---
title: "london"
author: "JustinJDavies"
date: "19 June 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rstan)
library(dplyr)
library(ggplot2)

rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

```

## Dataset

We have a response variable showing the total quotes per enquiry from a popular online price comparison website, grouped by London postcodes. A (not particularly) sample of (up to) 100 records for each London postcode district have been selected as a development dataset. Some postcode districts have fewer than 100 quotes in total.

```{r dataset}
d <- read.delim2('londonPostQuote', header = T)

summary(d %>% select(PostcodeArea, Quotes))

result <-   
    d %>% 
    group_by(PostcodeArea) %>% 
    mutate(pc2 = dense_rank(PostcodeOutward)) %>%
    mutate(pc1 = as.numeric(PostcodeArea)) %>% 
    ungroup() 

```

## Summary Plots

### Spatial plot (TODO)

<Place-holder for a map of London, coloured by postcode district>
https://cran.r-project.org/doc/contrib/intro-spatial-rl.pdf

### Total Quotes

It is possible that there is a systematic discrimination bewteen the quotability (number of quotes per enquiry) for each Postcode Area.

```{r postcode area, echo=FALSE}
boxplot(
    Quotes ~ PostcodeArea,
    data = result,
    notch = TRUE,
    col = (RColorBrewer::brewer.pal(n = max(unique(result$pc1)), name = "Set3"))
)
abline(h = mean(result$Quotes), col = "red")
title("Postcode District Average Quotes per Enquiry, grouped by Postcode Area")
```

It is not clear if this is driven by indiviual Postcode Districts.

```{r postcode district, echo=FALSE}

# See https://stackoverflow.com/questions/33221794/separate-palettes-for-facets-in-ggplot-facet-grid for charting tips & tricks
    areaAvgs <- result %>% group_by(PostcodeArea) %>% summarize(m = mean(Quotes))
    overallAvg <- result %>% summarize(m = mean(Quotes))

    ggplot(result, aes(fill=as.factor(pc1), x=as.factor(pc2), y=Quotes, group=pc2)) + 
    geom_boxplot() +
    geom_hline(data = areaAvgs, aes(yintercept = m), color="black", linetype="solid") +
    geom_hline(data = overallAvg, aes(yintercept = m), color="red", linetype="dashed") +
    scale_fill_manual(values = RColorBrewer::brewer.pal(n = 8, name = "Set3"), guide="none") +
    facet_wrap(~ PostcodeArea, ncol = 3) +
    ggtitle("QPE by Postcode District, faceted by Postcode Area") +
    theme(
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()
        )

```

## Model form

What is the best option for modelling the expected quotability of an enquiry, given the postcode area and district?

### Simple GLM

Indications from GLM analysis suggest that there are significant trends at both the Postcode Area and Postcode District level.

```{r simple glm, echo=TRUE}
g <- glm(
        formula = Quotes ~ PostcodeArea, 
        family = poisson(link = "log"),
        data = result
        )

summary(g)

```

If we fit (overfit) every postcode district, we can see that some are liklely significantly discriminated and some are not.

```{r overfit glm, echo=TRUE}
g <- glm(
        formula = Quotes ~ PostcodeOutward, 
        family = poisson(link = "log"),
        data = result
        )

summary(g)

```

How can we automatically balance between these two without extensive manual selection of postcode District parameters?

# stan ????

